---
title: "Data Management"
format: 
  pdf: 
    number-sections: true 
    toc: true            
    pdf-engine: xelatex   
editor: visual
---

```{r}
library(tidyverse)
library(descr)
library(knitr)
library(dplyr)
library(haven)
library(labelled)
```

```{r load-data}
file_path <- file.path("..","data","data_clean.sav")
```

```{r df}
df <- read_sav(file_path)
```

```{r}
head(df)
```

```{r}
library(descr)
```

```{r}
freq(as.ordered(df$gattAI2_8))
freq(as.ordered(df$job_anx_2))
freq(as.ordered(df$attitude2_1))
```

```{r}
sum(is.na(df$gattAI2_8))
sum(is.na(df$job_anx_2))
sum(is.na(df$attitude2_1))
```

The frequency tables above display the data regarding psychotherapists' desire to use AI in their job, their fear about becoming dependent on the technology and losing reasoning skills, and their belief as to whether or not AI incorporation is a good idea. The data rates the psychotherapists' responses from a scale of 1, meaning strongly disagree, to 5 or 7, meaning strongly agree.

The first frequency table shows that \~23% of those who answered the survey strongly disagree with having a desire to use AI in their practice, \~22% disagree, \~24% neither agree nor disagree, \~25 agree, and \~6% strongly agree. The second table shows that \~7% strongly disagree when asked if they fear becoming dependent on the technology, \~14% disagree, \~13% slightly disagree, \~11% neither agree nor disagree, \~31% slightly agree, \~17% agree, and \~7% strongly agree. The third table shows that \~26% strongly disagree with the sentiment that AI incorporation is a good idea, \~26% disagree, \~25% neither agree nor disagree, \~20% agree, and \~3% strongly agree.
